---
title: "TurismStats"
author: "Bengisu Oniz"
date: "24 Ekim 2017"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Turism Statistics of Turkey- The Departing visitors of Turkey

l wanted to analyze the Departing visitors of Turkey.l wanted to analyze the reasons of departures and the coutries that passengers travel from Turkey.  I downloaded the data from
[Turkish Statistical Institute](https://biruni.tuik.gov.tr/medas/?kn=74&locale=tr).

l downloaded the dataset from my files. Then l downloaded the packages tidyverse & dplyr. 

```{r}
install.packages(c("tidyverse"),repos="https://cran.r-project.org")
```


```{r}
library(dplyr)
```


```{r}
library("tidyverse") 
library("readxl")
```



```{r}
setwd("C:/Users/bengisu.oniz/Documents")
```


```{r}
turizmverileriexx<-read_excel("turizmverileriexx.xlsx",sheet=1) 

```


I wanted to see how my data looks like l used

```{r}
str(turizmverileriexx)
```

```{r}
head(turizmverileriexx)
```

The countries that passengers visited.
```{r}
totalpassengers<- turizmverileriexx %>% group_by(ulkeler) %>% summarise(toplam = sum(kisi_sayisi))

arrangedtotalpassengers <- totalpassengers %>% arrange(desc(toplam))

filtertotalpassengers  <- arrangedtotalpassengers %>% filter(ulkeler != "Türkiye" & ulkeler != "Ölçüm") %>% slice(1:10) 
```


```{r}
ggplot(data=filtertotalpassengers, aes(x=ulkeler, y=toplam)) +
  geom_bar(stat="identity",fill="blue")
```

The reasons that passengers' arrivals

```{r}
reasons<-turizmverileriexx %>% group_by(sebepler) %>% summarise(kisi_sayisi=sum(kisi_sayisi))
print(reasons)
```

```{r}

ggplot(data=reasons, aes(x=sebepler, y=kisi_sayisi)) +
  geom_bar(stat="identity",fill="red")
```

The countries that passengers travel for education.
```{r}
filtereducation<-turizmverileriexx %>% filter(sebepler=="Eðitim Staj (1 Yýldan Az, Kendisi Tarafýndan Ödenen)"& ulkeler != "Türkiye")%>%arrange(desc(kisi_sayisi))

```

```{r}
ggplot(data=filtereducation, aes(x=ulkeler, y=kisi_sayisi)) +
  geom_bar(stat="identity",fill="purple")
```

The reasons that passengers travel to Germany from Turkey.

```{r}
germanydata<-turizmverileriexx %>% filter(ulkeler=="Almanya")%>%arrange(desc(kisi_sayisi))
```


```{r}
ggplot(germanydata, aes(sebepler, kisi_sayisi)) +
  geom_bar(stat = "identity",fill="darkgreen") +
  coord_flip()

```
